Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-08-03 Documents/Paper/ms.tex
a --> w
URL, caching

In this section we apply
the DNS approach to a toy version of the problem of detecting and quantifying
extended objects such as galaxies in a noisy image.
We model each galaxy as a mixture of two concentric elliptical components, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. The radius of the
bigger gaussian is a parameter $a$.
Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the smaller gaussian
(therefore the fraction of the light in the bigger gaussian is $1-v$).
In a coordinate system aligned with the major axis of the ellipse, the
surface brightness profile of a ``galaxy'' is given by
\begin{eqnarray}
\rho(x, y) &=&
\frac{f(1-v)}{2\pi a^2}\exp\left[-\frac{1}{2a^2}\left(qx^2 + y^2/q\right)\right]
+\frac{fv}{2\pi (ua)^2}\exp\left[-\frac{1}{2(ua)^2}\left(qx^2 + y^2/q\right)\right]
\end{eqnarray}

@@

In general, it is possible to compute the number of components that have been
affected by the proposal. If this is greater than or equal to $N$, we compute
the mock signal from scratch, otherwise we subtract the effect of those
components that have been removed and add in the effect of those that have been
added.

>>>>

In this section we apply
the DNS approach to a toy version of the problem of detecting and quantifying
extended objects such as galaxies in a noisy image.
We model each galaxy as a mixture of two concentric elliptical components, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. The radius of the
bigger gaussian is a parameter $w$.
Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the smaller gaussian
(therefore the fraction of the light in the bigger gaussian is $1-v$).
In a coordinate system aligned with the major axis of the ellipse, the
surface brightness profile of a ``galaxy'' is given by
\begin{eqnarray}
\rho(x, y) &=&
\frac{f(1-v)}{2\pi w^2}\exp\left[-\frac{1}{2w^2}\left(qx^2 + y^2/q\right)\right]\\
&&+\frac{fv}{2\pi (uw)^2}\exp\left[-\frac{1}{2(uw)^2}\left(qx^2 + y^2/q\right)\right].
\end{eqnarray}

@@

In general, it is possible to compute the number of components that have been
affected by the proposal. If this is greater than or equal to $N$, we compute
the mock signal from scratch, otherwise we subtract the effect of those
components that have been removed and add in the effect of those that have been
added. In the C++ implementation of this work, available at
{\tt https://www.github.com/eggplantbren/RJObject/}, when a proposal takes
place, the difference between the old and new model is cached and is available
to the user, so that the likelihood can be updated rather than computed
from scratch.
